Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-11-19 paper/main.tex
16 pages

\begin{figure}[tp]
  \centering%
  \includegraphics[width=\textwidth]{../img/fitness_real_qap_kra32_dat}
    \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on the QAP instance \texttt{kra32}.\label{fig:kra32}}
\end{figure}

@@

In the LOP, differences are mostly in favour of UMM, due to the time limit of
144 hours, which resulted in CEGO typically achieving less than 200
evaluations. In contrast, UMM was always able to reach 400 evaluations in less
than 12.5 hours. If UMM was allowed to reach the 144 hours limit, the differences
would be even stronger.

In the case of the PFSP, the differences are minor and/or not statistically
significant, with the qualification that both algorithms appear to be
performing a random search. Similar observations can be made for the QAP, where
only on the smallest instance \texttt{nug12}, there is a significant difference
in favour of CEGO.

@@

 \caption{Mean fitness (and standard deviation) of the best solution found at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean of the difference between the fitness of UMM minus the one of CEGO. Mean runtime is measured in hours. If a run of  CEGO was not able to reach 400 function evaluations (FEs) in 144 hours, it was terminated earlier. This was the case for all LOP instances shown.\label{tab:results}}

@@

>>>>

\begin{figure}[tp]
  \centering%
  \includegraphics[width=\textwidth]{../img/fitness_real_qap_kra32_dat}
  \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on the QAP instance \texttt{kra32}.\label{fig:kra32}}
  \vspace*{-1em}
\end{figure}

@@

In the LOP, differences are mostly in favour of UMM, due to the time limit of
144 hours, which resulted in CEGO typically achieving less than 200
evaluations. In contrast, UMM was always able to reach 400 evaluations in less
than 12.5 hours. If UMM was allowed to reach the 144 hours limit, the differences
would be even stronger.
%
In the PFSP, the differences are minor and/or not statistically
significant, with the qualification that both algorithms appear to be
performing a random search. Similar observations can be made for the QAP, where
only on the smallest instance \texttt{nug12}, there is a significant difference
in favour of CEGO.

@@

  \caption{Mean fitness (and standard deviation) of the best solution found at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. Mean runtime is shown in hours. CEGO runs were stopped after 144 hours. This was the case for all LOP instances.\label{tab:results}}

@@

\vspace*{-1em}
